Appendix

### 2020-09-28 manuscript/article.tex
first edits after review

\title{The Effect of Legislature Size on Public Spending:\\ A Meta-Analysis\thanks{The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback. We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance. Replication materials are available at \url{https://github.com/danilofreire/distributive-politics-meta-analysis}. We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1) and from the FGV Applied Research Network.}}

@@

\author{Huzeyfe Alptekin\thanks{Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, Brazil, \url{huzeyfealptekin@gmail.com}.} \hspace{.5cm} Danilo Freire\thanks{Postdoctoral Research Associate, The Political Theory Project, Brown University, 8 Fones Alley, Providence, RI 02912, \url{danilofreire@gmail.com}, \url{http://danilofreire.github.io}. Corresponding author.} \hspace{.5cm} Umberto Mignozzetti\thanks{Assistant Professor, School of International Relations, Fundação Getulio Vargas, Brazil, \url{umberto.mignozzetti@fgv.br}, \url{http://umbertomig.com}.} \hspace{.5cm} Catarina Roman\thanks{Research Associate, School of International Relations, Fundação Getulio Vargas, Brazil, \url{catarinamroman@gmail.com}.}}

@@

\begin{abstract}
\noindent In a seminal article, \citet{weingast1981political} argue that there
is a positive relationship between legislature size and inefficiency in public
expenditures. Their proposition is currently known as the ``law of $1/n$'' and
has been widely cited by scholars in political science and public
administration.  However, recent studies have questioned the validity of the
theory. In this paper, we estimate the first meta-analysis of the relationship
between the number of legislators and public spending. Based on a sample of 26
empirical studies, we find little effect of legislature size on government
budgets. The available evidence suggests that, if such an effect exists, it is
driven by an increase in the upper chamber, but there is considerable
heterogeneity in the results. Our meta-regressions also indicate that study
coefficients vary significantly according to modelling specifications, such as
estimation method or variable selection.

@@

In this paper, we conduct the first meta-analysis that tests the generality of
the ``law of $1/n$''. We have selected 26 articles that use quantitative methods
to analyse the impact of legislature size over government spending. We run two
sets of models: the first group uses only the main estimates of each paper (36),
while the second set includes all coefficients reported in our sample
(126).\footnote{Although there are 26 papers in our review, we include 36
coefficients in the restricted sample. This is because 10 articles report
separate estimates for the impact of lower and upper house size on government
expenditures. In the full model, we added every outcome reported in the
paper, regardless of whether the coefficient comes from the main tables or
from robustness checks conducted by the original authors. We discuss our
sampling process in the Methods section of this paper and in the Supplementary
Material.} Our independent variables consist of three measures, namely the size
of the lower chamber ($n$), its natural logarithm (log($n$)), and the number of
members in the upper chamber ($k$). We evaluate their effect upon public
expenditure per capita, the natural logarithm of public expenditure per capita,
and government expenditure as a percentage of GDP. We then estimate if the
results vary according to four potential sources of effect heterogeneity.

Aggregate results show that council size has no significant impact on public
spending. Both the meta-analyses and the meta-regressions indicate that we
cannot generalise either the ``law of $1/n$'' or the ``reverse law of $1/n$''.
We find stronger evidence in favour of a positive impact of upper house size on
public budgets, yet the findings are not consistent in all of our estimations.
Our meta-regressions suggest that our study sample has a high level of
heterogeneity, and effects may differ substantially according to research design
specifications. In summary, our results point out that if legislature size
affects government budgets, they do so under specific conditions and are
mediated by domestic factors.

@@

OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional representation). Country codes follow the ISO 3166-1 alpha-3 international standard.}

@@

Most studies focus on the United States (12), but our sample also contains
papers on Australia (1), Brazil (1), Germany (2), Indonesia (1), Italy (1), and
Switzerland (2). Five articles use cross-national data and analyse from 2 to 110
countries. We also observe that although the ``law of $1/n$'' was first
formulated in 1981, the empirical assessment of the theory only started a few
years later, as dates of publishing range from 1998 to 2019.

>>>>

\title{The Effect of Legislature Size on Public Spending:\\ A Meta-Analysis\thanks{The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback. We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance. Replication materials are available at \url{https://github.com/danilofreire/distributive-politics-meta-analysis}. We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1).}}

@@

\author{Huzeyfe Alptekin\thanks{Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, Brazil, \href{mailto:huzeyfealptekin@gmail.com}{\texttt{huzeyfealptekin@gmail.com}}.}
\hspace{.5cm} Danilo Freire\thanks{Independent Researcher, \href{mailto:danilofreire@gmail.com}{\texttt{danilofreire@gmail.com}}, \url{http://danilofreire.github.io}. Corresponding author.} 
\hspace{.5cm} Umberto Mignozzetti\thanks{Visiting Assistant Professor, \href{mailto:umberto.mignozzetti@emory.edu}{\texttt{umberto.mignozzetti@emory.edu}}, \url{http://umbertomig.com}.} 
\hspace{.5cm} Catarina Roman\thanks{Research Associate, School of International Relations, Fundação Getulio Vargas, Brazil, \href{mailto:catarinamroman@gmail.com}{\texttt{catarinamroman@gmail.com}}.}}

@@

\begin{abstract}
\noindent In a seminal article, \citet{weingast1981political} argue that there
is a positive relationship between legislature size and inefficiency in public
expenditures. Their proposition is currently known as the ``law of $1/n$'' and
has been widely cited by scholars in political science and public
administration. However, recent studies have questioned the validity of the
theory. In this letter, we estimate the first meta-analysis of the relationship
between the number of legislators and public spending. Based on a sample of 26
empirical studies, we find little effect of legislature size on government
budgets. The available evidence suggests that, if such an effect exists, it is
driven by an increase in the upper chamber, but there is considerable
heterogeneity in the results. Our meta-regressions also indicate that study
coefficients vary significantly according to modelling specifications, such as
estimation method or variable selection.

@@

In this letter, we conduct the first meta-analysis that tests the generality of
the ``law of $1/n$''. We have selected 26 articles that use quantitative methods
to analyse the impact of legislature size over government spending. We run two
sets of models: the first group uses only the main estimates of each paper (36),
while the second set includes all coefficients reported in our sample
(126).\footnote{Although there are 26 papers in our review, we include 36
coefficients in the restricted sample. This is because 10 articles report
separate estimates for the impact of lower and upper house size on government
expenditures. In the full model, we add every outcome reported in the
papers, regardless of whether the coefficient comes from the main tables or
from robustness checks conducted by the original authors. We discuss our
sampling process in the Methods section of this paper and in the Supplementary
Material.} Our independent variables consist of three measures, namely the size
of the lower chamber ($n$), its natural logarithm (log($n$)), and the number of
members in the upper chamber ($k$). We evaluate their effect upon public
expenditure per capita, the natural logarithm of public expenditure per capita,
and government expenditure as a percentage of GDP. We then estimate if the
results vary according to four potential sources of effect heterogeneity.

Aggregate results show that council size has no significant impact on public
spending. Both the meta-analyses and the meta-regressions indicate that we
cannot generalise either the ``law of $1/n$'' or the ``reverse law of $1/n$''.
We find stronger evidence in favour of a positive impact of upper house size on
public budgets, yet the findings are not consistent in all of our estimations.
Our meta-regressions suggest that our study sample has a high level of
heterogeneity, and effects may differ substantially according to research design
specifications. We also find that recent studies, mainly those which employ
regression discontinuity designs, are more likely to find a negative association
between larger legislatures and public spending. In summary, our results point
out that if legislature size affects government budgets, they do so under
specific conditions and are mediated by domestic factors.

@@

OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
NM$=$Non-majoritarian (mixed or proportional representation). Country codes
follow the ISO 3166-1 alpha-3 international standard.}

@@

Our study sample reflects the development of the literature. Although the ``law
of $1/n$'' was first formulated in 1981, the empirical assessment of the theory
only started a few years later, as dates of publishing range from 1998 to 2019.

Most studies focus on the United States (12), but our sample also contains
papers on Australia (1), Brazil (1), Germany (2), Indonesia (1), Italy (1), and
Switzerland (2). Five articles use cross-national data and analyse from 2 to 110
countries.
